---
title: "cdc_zika_colombia"
author: "Daniel Chen"
date: "March 24, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)

setwd('~/git/vbi/zika_dashboard_cdc/')

files <- list.files(path = '../zika/',
                    pattern = '[0-9]{4}-[0-9]{2}-[0-9]{2}.csv$',
                    recursive = TRUE,
                    full.names = TRUE)

tables <- lapply(files, readr::read_csv)

combined_df <- do.call(rbind , tables)

rm(files, tables)

parsed_location <- combined_df %>%
    tidyr::separate(col = location,
                    into = c('country', 'location2', 'location3'),
                    sep = '-',
                    fill = 'right')
```

```{r}
colombia <- parsed_location %>%
    dplyr::filter(country == 'Colombia')
```

```{r}
colombia$data_field %>% unique()

colombia$location2 %>% unique()

colombia$location3 %>% unique()
```

```{r}
cumulative_country <-
    colombia %>%
    dplyr::mutate(value = as.numeric(value)) %>%
    dplyr::group_by(report_date, country) %>%
    summarize(cum_sum = sum(value))
```

```{r}
ggplot(data = cumulative_country, aes(x = as.Date(report_date), y = cum_sum)) +
    geom_line() +
    ylim(0, 50000)
```


```{r}
cumulative_country_2 <-
    colombia %>%
    dplyr::mutate(value = as.numeric(value)) %>%
    dplyr::group_by(report_date, country, location2) %>%
    summarize(cum_sum = sum(value))
```

```{r}
ggplot(data = cumulative_country_2, aes(x = as.Date(report_date), y = cum_sum)) +
    geom_line(aes(color=location2)) +
    ylim(0, 10000)
```
```


```{r}
cumulative_country_3 <-
    colombia %>%
    dplyr::mutate(value = as.numeric(value)) %>%
    dplyr::group_by(report_date, country, location2, location3) %>%
    summarize(cum_sum = sum(value))
```

```{r}
ggplot(data = cumulative_country_3, aes(x = as.Date(report_date), y = cum_sum)) +
    geom_line(aes(color=location3)) +
    theme(legend.position="none")
```

```{r}
ggplot(data = cumulative_country_3, aes(x = as.Date(report_date), y = cum_sum)) +
    geom_line(aes(color=location3)) +
    theme(legend.position="none") +
    facet_wrap(~location2, scales='free')
```


